A Plasma Torus Around a Young Low-Mass Star

### 2025-01-26 paper/ms.tex
update

\begin{figure}[!b]
  \centering
  \includegraphics[width=0.99\textwidth]{figures/sf1.pdf}
  \caption{Detailed photometric evolution of TIC 141146667 near the
  epoch of spectroscopic observation (green bar). 
  {\bf Panel a}: TESS simple aperture photometry acquired
  near time of Keck/HIRES observation.  The main data gaps were caused
  by scattered light from the Earth and Moon, respectively.
  {\bf Panels b,c}: Folded light curve before and after spectroscopy.
  While some evolution in the detailed light curve morphology occurred
  between the two epochs, the large, complex eclipse feature remained
  present.
  }
  \label{fig:fulllc}
\end{figure}

@@

{\it Age: No Obvious Association Membership}---Previous work
\cite{Bouma2024} has shown that over 90\% of CPVs are associated with
known young moving groups based on their positions and kinematics.
TIC~141146667 is one of the exceptions.  We calculated the probability
of TIC~141146667 being part of any of the nearby known groups using
BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018}, and based on that model,
it appears to be a field star at $>$99.9\% confidence.  Searching the
local vicinity of the star for neighbors with similar projected on-sky
velocity \cite{Tofflemire2021} similarly yields no strong candidates
for co-moving ($\Delta v_{\rm T}$$<$5\,\kms) stars that share its
isochronal youth.

>>>>

\begin{figure}[!b]
  \centering
  \includegraphics[width=0.99\textwidth]{figures/sf1.pdf}
  \caption{Photometric evolution of TIC 141146667 near the epoch of
  spectroscopic observation (green bar). 
  {\bf Panel a}: TESS simple aperture photometry. 
  The main data gaps were caused by scattered light from the Earth
  (BTJD 3356-3358.5) and Moon (BTJD 3359.5-3360.5).
  {\bf Panels b,c}: Folded light curve before and after spectroscopy.
  While some evolution in the light curve morphology occurred between
  the two epochs, the large, complex eclipse feature remained present.
  }
  \label{fig:fulllc}
\end{figure}

@@

{\it Age: No Obvious Association Membership}---Previous work
\cite{Bouma2024} has found over 90\% of CPVs to be associated with
known young moving groups based on their positions and kinematics.
TIC~141146667 is one of the exceptions.  We calculated the probability
of TIC~141146667 being part of any of the nearby known groups using
BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  Based on that model,
it appears to be a field star at $>$99.9\% confidence.  Searching the
local vicinity of the star for neighbors with similar projected on-sky
velocity \cite{Tofflemire2021} similarly yields no strong candidates
for co-moving stars --- defined as those with projected tangential
velocities $\Delta v_{\rm T}$$<$5\,\kms --- that share its isochronal
youth.
